Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper2.tex
fix mu_R typos

\subsection{Renormalisation scale dependence}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fame2/renormalisation_scale_trajectories_logscale.pdf}
    \caption{Renormalisation scale trajectories for all multiplicities.
    These trajectories are predictions of the k-factor with the sum
    of antenna functions subtracted to show renormalisation scale
    dependence in the remainder. Each trajectory is at one phase-space point
    sampled from {\RAMBO}, with $\mu_{R}$ spanning the range
    $[s_{\mathrm{com}}/8, 8 s_{\mathrm{com}}]$. Each trajectory
    is composed of 1000 points.
    The region that $\mu_{R}$ was uniformly sampled from
    for training is indicated as a red band. The error bands on the NN
    predictions are too small to be seen.}
    \label{fig:1L_mu_trajectory}
\end{figure}

In Figure~\ref{fig:1L_mu_trajectory} we show that our
emulator has learned the renormalisation scale dependence,
independent of the antenna functions. To produce
a trajectory we first sample a phase-space point with
the same cuts as described in Section~\ref{sec:1L_nn}, then we
evaluate the k-factor at this phase-space point with $\mu_{R}$
varying from $s_{\mathrm{com}}/8$ to $8s_{\mathrm{com}}$.
We choose to sample from a wider range than used for training
to examine the $\mu_{R}$ extrapolation performance.
After subtracting the sum of the antenna functions we see that the
remainder still has a dependence on the renormalisation
scale that is accurately captured by the neural network.
As with the $\Delta$ distribution plots in Figure~\ref{fig:1L_delta_distribution},
there is a slight decrease in accuracy as we increase the
multiplicity, however, the ratios and differences are well-behaved
throughout the entirety of the trajectories inside the
range of training data. The only anomaly occurs when the
trajectories cross zero, causing spikes in the ratios,
but the difference in truth and prediction remains well-behaved
around these regions. Outside of the training
range we see an acceptable extrapolation, but given that
the training range is wider than the range in which the
renormalisation scale is normally varied for scale
variations, we do not find this problematic.

>>>>

\subsection{Renormalisation scale dependence}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fame2/renormalisation_scale_trajectories_logscale.pdf}
    \caption{Renormalisation scale trajectories for all multiplicities.
    These trajectories are predictions of the k-factor with the sum
    of antenna functions subtracted to show renormalisation scale
    dependence in the remainder. Each trajectory is at one phase-space point
    sampled from {\RAMBO}, with $\mu_{R}$ spanning the range
    $[\sqrt{s_{\mathrm{com}}}/8, 8 \sqrt{s_{\mathrm{com}}}]$. Each trajectory
    is composed of 1000 points.
    The region that $\mu_{R}$ was uniformly sampled from
    for training is indicated as a red band. The error bands on the NN
    predictions are too small to be seen.}
    \label{fig:1L_mu_trajectory}
\end{figure}

In Figure~\ref{fig:1L_mu_trajectory} we show that our
emulator has learned the renormalisation scale dependence,
independent of the antenna functions. To produce
a trajectory we first sample a phase-space point with
the same cuts as described in Section~\ref{sec:1L_nn}, then we
evaluate the k-factor at this phase-space point with $\mu_{R}$
varying from $\sqrt{s_{\mathrm{com}}}/8$ to $8\sqrt{s_{\mathrm{com}}}$.
We choose to sample from a wider range than used for training
to examine the $\mu_{R}$ extrapolation performance.
After subtracting the sum of the antenna functions we see that the
remainder still has a dependence on the renormalisation
scale that is accurately captured by the neural network.
As with the $\Delta$ distribution plots in Figure~\ref{fig:1L_delta_distribution},
there is a slight decrease in accuracy as we increase the
multiplicity, however, the ratios and differences are well-behaved
throughout the entirety of the trajectories inside the
range of training data. The only anomaly occurs when the
trajectories cross zero, causing spikes in the ratios,
but the difference in truth and prediction remains well-behaved
around these regions. Outside of the training
range we see an acceptable extrapolation, but given that
the training range is wider than the range in which the
renormalisation scale is normally varied for scale
variations, we do not find this problematic.
